%!TEX program = xelatex
\documentclass[12pt,a4paper]{article}

% Packages
\usepackage[left=0.5in,right=0.5in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{fontspec}
\usepackage{amsmath}

\setmainfont{Arial}
\setsansfont{Arial}

\hypersetup{colorlinks=false, pdfborderstyle={/S/U/W 0}}

\definecolor{headerblue}{RGB}{49,25,83}
\definecolor{sectionblue}{RGB}{49,25,83}
\definecolor{separatorcolor}{RGB}{49,25,83}

\titleformat{\section}{\large\bfseries\color{sectionblue}}{}{0em}{\MakeUppercase}[\color{sectionblue}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{4pt}
\definecolor{companycolor}{RGB}{90,90,90}


\pagestyle{empty}

\begin{document}

% ─────────────────────────────────────────────
%  PAGE 1 — GET THE INTERVIEW
% ─────────────────────────────────────────────

\begin{center}
    {\Huge\bfseries\color{headerblue} A.M. Rinas}\\[5pt]
    {\LARGE\color{headerblue} JAVA SOFTWARE ENGINEER}
\end{center}

\vspace{6pt}

\noindent{\normalsize
\begin{minipage}[t]{0.18\textwidth}
+94 76 5596863
\end{minipage}%
{\color{separatorcolor}\textbf{$\boldsymbol{|}$}}\hspace{0.01\textwidth}%
\begin{minipage}[t]{0.21\textwidth}
\centering
\href{https://rinas21.github.io/amrinas/}{\faUser}\;
\href{https://www.linkedin.com/in/amrinas/}{\faLinkedin}\;
\href{https://github.com/rinas21}{\faGithub}\;
\href{https://www.youtube.com/@amrinas}{\faYoutube}\;
\href{https://qamastery.blogspot.com}{\faBlog}
\end{minipage}%
{\color{separatorcolor}\textbf{$\boldsymbol{|}$}}\hspace{0.01\textwidth}%
\begin{minipage}[t]{0.33\textwidth}
\centering
mohomadrinas00@gmail.com
\end{minipage}%
{\color{separatorcolor}\textbf{$\boldsymbol{|}$}}\hspace{0.01\textwidth}%
\begin{minipage}[t]{0.22\textwidth}
\raggedleft
Colombo, Sri Lanka
\end{minipage}
}

\vspace{4pt}
{\color{separatorcolor}\noindent\rule{\textwidth}{0.6pt}}
\vspace{2pt}

% ── Profile ──────────────────────────────────
\section*{PROFILE}
Software Engineer with hands-on experience developing enterprise applications using Java, Servlets, REST APIs, Node.js, React, and TypeScript. Experienced in building backend services, implementing business workflows, integrating databases, and supporting production systems in telecom, \\banking, and business domains. Skilled in API development, SQL-based applications, Docker-based environments, Git workflows, and Agile software development with a focus on delivering reliable and maintainable software solutions.
\vspace{6pt}

% ── Work Experience ───────────────────────────
\section*{WORK EXPERIENCE}

% 1. Wincore
\noindent\textbf{Full Stack Software Engineer (Consultant)} \hfill Feb 2026 -- Present\\
\textit{Wincore Pvt Ltd, Colombo}

\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=3pt]

\item Developed and integrated Node.js backend services, REST APIs, database operations, and \\Docker-based development environments.

\item Designed API-driven application workflows, authentication flows, and data interactions between frontend applications and backend systems.

\item Built and maintained full stack web applications using React, Next.js, TypeScript, SQL databases, and REST API integrations.

\item Investigated and resolved production issues across application, API, and deployment layers.

\end{itemize}

\vspace{6pt}

% 2. hSenid — SE Trainee
\noindent\textbf{Software Engineer Trainee} \hfill Dec 2024 -- Feb 2026\\
\textit{hSenid Mobile Solutions (Pvt) Ltd, Colombo}

\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=3pt]
   \item Developed and maintained enterprise web applications using Java, MVC architecture, Servlets, REST APIs, and SQL databases, implementing business logic and backend workflows.
\item Designed and developed RESTful backend services for a Mobile Number Portability system, \\implementing business validations, database operations, and third-party API integrations.
\item Developed backend features for Merchant Management systems using Java and Node.js, \\implementing API integrations, transaction workflows, and database operations.
\item Participated in Agile development, code reviews, CI/CD pipelines, production deployments, and issue resolution using Git, Tomcat, and Docker-based development environments.
\end{itemize}

\vspace{6pt}

% 3. hSenid — QA Intern
\noindent\textbf{Software Quality Assurance Intern} \hfill Jan 2024 -- Nov 2024\\
\textit{hSenid Mobile Solutions (Pvt) Ltd, Colombo}

\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=3pt]
    \item Performed API, functional, and security testing on enterprise Java applications in telecom and banking domains.
    \item Tested Event Management and Merchant Management systems across UI, API, and database layers.
    \item Built test automation scripts and SQL queries to support repeatable QA processes.
\end{itemize}

\newpage

% ─────────────────────────────────────────────
%  PAGE 2 — SUPPORT THE CLAIMS
% ─────────────────────────────────────────────\section*{PROJECTS}
\noindent\textbf{Mobile Number Portability System}
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]

\item Developed Java Servlet-based backend services for processing mobile number portability requests, implementing business validation logic and telecom workflows.

\item Built and maintained REST APIs with MySQL database operations following MVC architecture, supporting integration between distributed systems.

\item Investigated and resolved production issues, improving system reliability and performance.

\item \textbf{Stack:} Java, Servlets, MySQL, REST APIs, Shell Scripting, Postman

\end{itemize}

\vspace{3pt}
\noindent\textbf{Customer Segmentation \& Rewarding System}
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]

\item Developed backend components for a banking rewards platform, implementing customer eligibility rules, transaction processing, and reporting workflows.

\item Integrated REST APIs and SQL-based data operations for enterprise banking services, supporting secure customer and transaction management.

\item Investigated production issues and implemented backend enhancements to improve application stability.

\item \textbf{Stack:} Java, IBM Db2, REST APIs, Node.js, GraphQL

\end{itemize}
\vspace{3pt}
\noindent\textbf{Campaign Management System}
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]

\item Developed Java-based campaign processing logic for telecom reward campaigns based on \\customer transaction and usage profiles.

\item Optimized SQL queries and resolved production issues, improving backend performance and \\operational stability.

\item Collaborated using Git-based development workflows within an Agile team.

\item \textbf{Stack:} Java, Servlets, JavaScript, Maven, Bash

\end{itemize}
\vspace{5pt}

% ── Technical Skills ──────────────────────────
\section*{TECHNICAL SKILLS}

\noindent\textbf{Languages:} Java, JavaScript, Python, SQL, Bash

\vspace{3pt}

\noindent\textbf{Backend:} Java, Servlets, Node.js, REST APIs
\vspace{3pt}

\noindent\textbf{Frontend:} React, Next.js, HTML/CSS, JavaScript, TypeScript

\vspace{3pt}

\noindent\textbf{Databases:} PostgreSQL, MySQL, IBM Db2, MongoDB

\vspace{3pt}

\noindent\textbf{Testing:} API Testing, Functional Testing, Test Automation

\vspace{3pt}

\noindent\textbf{DevOps \& Tools:} Git, Docker, CI/CD, Linux, Tomcat, Nginx, Postman, GCP, Oracle Cloud

\vspace{8pt}

% ── Education ────────────────────────────────
\section*{EDUCATION}

\noindent\textbf{B.Sc. (Hons.) in Software Engineering} \hfill 2026\\
The Open University of Sri Lanka (GPA: 3.76)

\vspace{5pt}
\section*{CERTIFICATIONS}

\noindent\textbf{Linux Systems Administration and DevOps Engineering} 
\hfill {\color{companycolor}\textbf{WSO2}}\\
Linux administration, Docker, Ansible, CI/CD, networking, automation, and DevOps practices.

\vspace{6pt}

\noindent\textbf{Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate} 
\hfill {\color{companycolor}\textbf{Oracle}}\\
Cloud fundamentals, OCI services, AI concepts, and machine learning foundations.

\vspace{6pt}

\noindent\textbf{Python Programming} 
\hfill {\color{companycolor}\textbf{University of Moratuwa}}\\
Python programming fundamentals, data structures, algorithms, and application development.

\end{document}
